Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-09 minimax.tex
qC, not p

\subsection{Value of information comparison}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
			\midrule
			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
			15 & 0.71 & 0.73 & 0.67	& 0.64 \\
			30 & 0.62 & 0.5 & 0.8 & 0.62 \\
			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
			100 & 2.03 & 1.56 & 1.88 & 1.02  \\
			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
			200 & 4.61	& 1.35  & 6.53 & 2.0  \\
			250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
			300 &11.07 & 0.86& 11.87 & 1.25 \\
			350 &15.06 & 0.68&15.59 & 0.6 \\
			400 &20.0 & 0.0 & 20.0 & 20.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions. Where $p$ represents the number of questions asked to the chair.}
	\label{tab:twoP400}
\end{table}

>>>>

\subsection{Value of information comparison}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
			\midrule
			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
			15 & 0.71 & 0.73 & 0.67	& 0.64 \\
			30 & 0.62 & 0.5 & 0.8 & 0.62 \\
			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
			100 & 2.03 & 1.56 & 1.88 & 1.02  \\
			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
			200 & 4.61	& 1.35  & 6.53 & 2.0  \\
			250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
			300 &11.07 & 0.86& 11.87 & 1.25 \\
			350 &15.06 & 0.68&15.59 & 0.6 \\
			400 &20.0 & 0.0 & 20.0 & 20.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
	\label{tab:twoP400}
\end{table}
